---
title: "Introduction to FARS functions"
author: "Mathieu Jones"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Intro

This package is a simple example package that I'm putting up on github as part of the R course on coursera.org.

The functions that are exported as part of this package have to do with manipulating data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System. This is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. 

# Sample functions

First, we load the functions.

```{r}
devtools::load_all()
library(dplyr)
```

Below, I give two examples of the use of these functions.

## summarise years function

The summarise years functions reads in the csv for the FARS data for a particular year. It then summarises the number of fatal crashes per month in those years. The below example illustrates for the years 2013 and 2014.

```{r}

# setwd("../data")
fars_summarize_years(c(2013,2014))

```


## fars map function

This function will plot all the accidents in a given state for a given year.

```{r}
# setwd("../data")
fars_map_state(1, 2013)

```
